A Study on Penguins: A Minimal Reproducible Example

### 2024-04-29 01_Example/Manuscript.qmd
created pdf

---
title: "A Study on Penguins: A Minimal Reproducible Example"
author:
  - name: "Kan Garoo"
    affiliation: "University of Melbourne"
    email: "kangaroo@email.com"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  quarto::apa_document
bibliography: Bibliography.bib
---

>>>>

---
title: "A Study on Penguins: A Minimal Reproducible Example"
author:
  - name: "Kan Garoo"
    affiliation: "University of Melbourne"
    email: "kangaroo@email.com"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
bibliography: Bibliography.bib
format:
  #apaquarto-docx: default
  #apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    keep-tex: true
---
